---
title: "Open University Learning Analytics Dataset Exploration"
author: "Intan Dea Yutami"
date: "22 Februari 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo = FALSE, message=FALSE}
    library(ggplot2)
    library(dplyr)
    studInfo <- read.csv("studentInfo.csv")
```
## Brief Description of App

This application is based on Open University Learning Dataset. The dataset is taken from:
<https://archive.ics.uci.edu/ml/datasets/Open+University+Learning+Analytics+dataset#>

The dataset contains data about courses, students and their interactions with Virtual Learning Environment (VLE) for seven selected courses (called modules).

This application reads the file: studentInfo.csv, which stores the information of final result of the assessment from the seven courses, done by students enrolled in those courses.

The following result is the columns inside studentInfo.csv.

```{r echo=TRUE}
#studInfo <- read.csv("studentInfo.csv")
head(studInfo)
```

## Tab 1 : General Passing Rate

This tab is basically showing the relationship between number of students passing the assessment and two other variables selected by the user. User also enters a specific number as sample size to subset the dataset.  

Student is considered passed if his/her final result is either 'Passed' or 'Distinction'. Below is the example of plot from 500 random samples taken from the dataset.

Just choose a number to set as sample size on the left panel, and select two other variables to explore the relationship!

```{r echo = TRUE, message = FALSE}

    new_df <- studInfo[sample(nrow(studInfo), 1000), ]
    new_df$isPassed <- ifelse(new_df$final_result == "Distinction" |
                                            new_df$final_result == "Pass", 1, 0)
    new_df$gender <- as.factor(new_df$gender)
    new_df$region <- as.factor(new_df$region)
    sum_table <- group_by(new_df, gender, region) %>% summarize(isPassed = sum(isPassed))
    
    p <- ggplot(sum_table, aes(region, isPassed, fill = region)) + geom_bar(stat = "identity")
    input_x1 <- toupper("Region")
    p <- p + ggtitle("Total Passing Students by Gender and Region ") + facet_grid( . ~ gender) + scale_x_discrete(labels = abbreviate) + theme(axis.text.x = element_text(angle = 90, hjust = 1))  + labs(y = "Total Students Passed", x = "") + guides(fill=guide_legend(title=paste("", input_x1)))
    print(p)
```

## Tab 2 : Course-Based Passing Result

This tab is showing the relationship between final result of the assessment and a variable picked by user from a specific course. Below is an example of the plot.

To see the plot, choose a course and a parameter to relate to final result of the assessment.

```{r echo = TRUE, message = FALSE}
    infoModule <- studInfo[studInfo$code_module == "CCC",]
    count_res <- table(infoModule$final_result, infoModule$highest_education)
    colorList <- c("darkblue", "red", "darkgreen", "gold")                                      
    par(mar=c(10.1, 4.1, 2.1, 8.1), xpd=TRUE)
    barplot(count_res, 
            main="Final Result Distribution by Highest Education from course CCC", 
            ylab = "Number of Students", las = 2,
            col=colorList
    )
    legend("topright", inset=c(-0.1,0),
           legend = rownames(count_res),
           fill = colorList
    )
```

## Relevant Links

Github: <https://github.com/intandeay/ddp_oulad>

Shiny application: <https://intandea.shinyapps.io/ddp_oulad/>

Open University Learning Analytics Dataset: <https://analyse.kmi.open.ac.uk/open_dataset>

